% Section 5: Specification III — RAIF Structural Requirements

\section{Specification III: RAIF Structural Requirements}
\label{sec:raif}

\subsection{The RAIF Regime}
\label{sec:raif-regime}

The Reserved Alternative Investment Fund (RAIF) was introduced by Luxembourg law in 2016. A RAIF combines the regulatory flexibility of an unregulated vehicle with the legal certainty of a dedicated statute. Key features:

\begin{itemize}
  \item \textbf{No CSSF authorization}: Unlike SIFs or Part II UCIs, RAIFs are not authorized by the regulator. They must only file with CSSF for statistical purposes.
  \item \textbf{Mandatory AIFM}: Every RAIF must appoint an authorized AIFM (internal or external).
  \item \textbf{Investor restriction}: Only ``well-informed investors'' may invest.
  \item \textbf{Flexible legal form}: RAIFs may take various corporate or contractual forms.
\end{itemize}

\subsection{Legal Form Options}
\label{sec:legal-forms}

\begin{lstlisting}
declaration enumeration LegalForm:
  -- SICAV_SA
  -- SICAV_SCA
  -- SICAV_Sarl
  -- SICAF_SA
  -- SICAF_SCA
  -- SICAF_Sarl
  -- FCP
  -- SCS
  -- SCSp
\end{lstlisting}

The \textbf{SCSp} (Société en Commandite Spéciale) form is particularly popular for private equity and venture capital structures due to its flexibility and tax transparency. It closely mirrors Anglo-American limited partnerships.

\subsection{Structural Compliance Check}
\label{sec:raif-compliance}

We define a structure capturing RAIF requirements:

\begin{lstlisting}
declaration structure RAIFStructure:
  data legal_form content LegalForm
  data establishment_jurisdiction content text
  data aifm_type content AIFMType
  data aifm_is_authorized content boolean
  data depositary_appointed content boolean
  data depositary_jurisdiction content text
  data cssf_filing_complete content boolean
  data all_investors_well_informed content boolean
  data offering_document_prepared content boolean
\end{lstlisting}

The compliance scope performs a structural check:

\begin{lstlisting}
scope RAIFCompliance:
  definition is_compliant equals
    fund.establishment_jurisdiction = "Luxembourg"
    and fund.aifm_is_authorized
    and fund.depositary_appointed
    and (fund.depositary_jurisdiction = "Luxembourg" 
         or fund.depositary_jurisdiction = "EU")
    and fund.cssf_filing_complete
    and fund.all_investors_well_informed
    and fund.offering_document_prepared

  definition compliance_failures equals
    (if not (fund.establishment_jurisdiction = "Luxembourg")
     then ["FAILURE: RAIF must be established in Luxembourg"]
     else [])
    ++ [... additional checks ...]
\end{lstlisting}

\subsection{AIFM Delegation Requirements}
\label{sec:delegation}

When a RAIF uses an external AIFM, delegation rules apply. The AIFM may delegate portfolio management or risk management, but:

\begin{itemize}
  \item Both functions cannot be delegated to the same entity
  \item The AIFM must maintain oversight
  \item Material delegations must be notified to CSSF
\end{itemize}

\begin{lstlisting}
scope AIFMDelegationCompliance:
  definition delegation_valid equals
    delegation.aifm_maintains_oversight
    and (not delegation.both_delegated_to_same_entity 
         or not (delegation.portfolio_management_delegated 
                 and delegation.risk_management_delegated))
\end{lstlisting}

\subsection{Commentary}
\label{sec:raif-commentary}

\paragraph{Structural Simplicity:} The RAIF structure is relatively straightforward to formalize because most requirements are binary checks:
\begin{itemize}
  \item Is there an authorized AIFM?
  \item Is there a depositary?
  \item Are all investors well-informed?
\end{itemize}

\paragraph{Areas Requiring Judgment:}
\begin{enumerate}
  \item \textbf{``Authorized'' AIFM}: The specification checks a boolean, but determining whether an AIFM is validly authorized requires verification against CSSF registers and assessment of passport validity.
  \item \textbf{``Well-informed'' Investors}: Cross-references to the professional investor specification. Each investor must be individually assessed.
  \item \textbf{Offering Document}: The specification checks existence, not adequacy. Whether the offering document meets disclosure requirements is qualitative.
\end{enumerate}

\paragraph{Temporal Considerations:} This specification is a point-in-time check. In practice:
\begin{itemize}
  \item CSSF filing must occur within 1 month of RAIF launch
  \item Annual reports must be filed within 6 months of year-end
  \item Investor status should be verified at each subscription
\end{itemize}

A complete implementation would need to track these temporal obligations.
