% Section 6: Specification IV — Cross-Reference Verification

\section{Specification IV: Cross-Reference Verification}
\label{sec:crossref}

\subsection{The Problem}
\label{sec:crossref-problem}

A fund structure contains multiple documents with overlapping definitions. For example, ``Permitted Investments'' may be defined in:

\begin{itemize}
  \item The LPA (Schedule 3)
  \item The Offering Memorandum (Section 4)
  \item The AIFM Agreement (Exhibit B)
\end{itemize}

These definitions \textit{should} be consistent. In practice, they often diverge through:

\begin{itemize}
  \item Drafting by different teams (LPA by fund counsel, OM by placement agent's counsel)
  \item Amendments not propagated across documents
  \item Deliberate variation (the OM is marketing; the LPA is binding)
\end{itemize}

\subsection{Real Example}
\label{sec:crossref-example}

In a recent fund review, the author found:

\begin{quote}
\textbf{LPA:} ``Permitted Investments include debt instruments rated at least BBB- by S\&P or equivalent.''

\textbf{OM:} ``Permitted Investments include investment grade debt instruments.''
\end{quote}

These are \textit{not} equivalent. BBB- is the \textit{lowest} investment grade rating. The LPA is more specific; the OM is broader. An instrument rated BBB by Moody's but not rated by S\&P could arguably fall within the OM definition but outside the LPA definition.

This inconsistency creates:
\begin{itemize}
  \item \textbf{Compliance risk}: Is an unrated instrument permitted?
  \item \textbf{Marketing risk}: The OM promises broader scope than the LPA allows
  \item \textbf{Investor disputes}: Which document governs?
\end{itemize}

\subsection{The Catala Specification}
\label{sec:crossref-spec}

We define structures to capture investment restrictions:

\begin{lstlisting}
declaration structure DebtRatingCriterion:
  data rating_agency_specified content boolean
  data specific_agency content text
  data minimum_rating_specified content boolean
  data minimum_rating content text
  data uses_generic_term content boolean

declaration structure PermittedInvestmentDef:
  data document_source content text
  data includes_debt_instruments content boolean
  data debt_rating_criterion content DebtRatingCriterion option
  data geographic_restrictions content list of text
  data maximum_leverage content decimal option
\end{lstlisting}

The consistency check scope:

\begin{lstlisting}
scope DefinitionConsistency:
  definition debt_rating_lpa_om_consistent equals
    match (def_lpa.debt_rating_criterion, 
           def_om.debt_rating_criterion) with pattern
    -- (Some lpa_crit, Some om_crit):
      if lpa_crit.uses_generic_term and 
         om_crit.uses_generic_term then true
      else if lpa_crit.minimum_rating_specified and 
              om_crit.uses_generic_term then false
      else lpa_crit.minimum_rating = om_crit.minimum_rating
    -- (None, None): true
    -- _: false
\end{lstlisting}

\subsection{Severity Classification}
\label{sec:crossref-severity}

We classify inconsistencies by severity:

\begin{lstlisting}
  # Default: no issues
  definition severity equals None

  # Low: geographic differences (may be intentional)
  exception definition severity equals Low
    under condition not geo_consistent
      and debt_rating_lpa_om_consistent

  # Medium: leverage differences
  exception definition severity equals Medium
    under condition not leverage_consistent
      and debt_rating_lpa_om_consistent

  # High: rating inconsistencies (compliance risk)
  exception definition severity equals High
    under condition not debt_rating_lpa_om_consistent
\end{lstlisting}

\subsection{Commentary}
\label{sec:crossref-commentary}

\paragraph{What This Demonstrates:}
\begin{itemize}
  \item Automated detection of definition inconsistencies
  \item Severity classification to prioritize review
  \item Traceability to specific documents and provisions
\end{itemize}

\paragraph{Limitations:}
\begin{enumerate}
  \item \textbf{Encoding cost}: Requires all documents to be encoded in structured form---a massive upfront investment
  \item \textbf{Semantic limits}: Cannot detect semantic equivalence, only structural matching
  \item \textbf{Intentional variation}: Some inconsistencies are deliberate (the OM may use marketing-friendly language)
\end{enumerate}

\paragraph{The Key Insight:} This is NOT about eliminating human judgment. It is about \textit{locating} where documents diverge, so humans can determine whether the divergence is:
\begin{itemize}
  \item Acceptable (intentional simplification for marketing)
  \item Problematic (drafting error creating ambiguity)
  \item Critical (binding terms that contradict each other)
\end{itemize}

The specification surfaces the question. The lawyer answers it.
